---
output: pdf_document
---
Developing Data Products - Shiny App Course Project 
======================================

####Emanuele Pellichero 7/29/2016

##Child's Adult Height Predictor 


### 1. Introduction

This shiny app was created for the final project of the Coursera Developing Data Products class from Johns Hopkins University. As part of this assignement a web app was created to predict an outcome using a number of predictors from a known dataset.

This Application predicts the adult's height of a child based on the height of the parents and the gender of the child. The predictor function is based on the Galton dataset,  which is a dataset that was used by Galton in 1885 to study the correlation between the parent\'s height and their children.
    

### 2. The GaltonFamilies dataset

The Galton dataset contains data from 934 adult children born to 205 fathers and mothers. The dataset has 8 variables,

* *family*: family ID, a factor with levels 001-204

* *father*: height of father

* *mother*: height of mother

* *midparentHeight*: mid-parent height, calculated as (father + 1.08mother)/2

* *children*: number of children in this family

* *childNum*: number of this child within family. Children are listed in decreasing order of height for boys followed by girls

* *child gender*: a factor with levels female male

* *childHeight*: height of child

here below is the database summary:

```{r, echo=FALSE,message=FALSE, comment=FALSE,warning=FALSE}

library(HistData)

data("GaltonFamilies")

summary(GaltonFamilies)
```

### 3. The predictor function

The child's adult height was predicted by fitting a linear regression model to the Galton dataset, using *childHeight* as the outcome and *midparentHeight* and *gender* as predictors. Other variables from the dataset were omitted in the linear regression as they appeared to not have a positive effect on the accuracy of the prediction  (See Fig.2 below) The regression model is shown below:

```{r, message=FALSE, comment=FALSE,warning=FALSE}

fit <- lm(childHeight ~ midparentHeight + gender,data=GaltonFamilies)

summary(fit)
```

**Figure 1** - Chart with the regression model:


```{r, echo=FALSE, message=FALSE, comment=FALSE,warning=FALSE}
library(ggplot2)

ggplot(GaltonFamilies, aes(x = midparentHeight, y = childHeight, colour=gender)) + 
  geom_point() +
  geom_smooth(method = "lm")

```

**Figure 2** - Pair Wise plot for the variables in the dataset. *family* was omitted as it is just an ID and *father* and *mother* were omitted as they  are obviously cooreleted to *midparentHeight*.

```{r, echo=FALSE, message=FALSE, comment=FALSE,warning=FALSE}
library(GGally)

ggpairs(GaltonFamilies,columns=4:8)

```


### 4. The shiny app

####*The shiny app is available [here](https://pell.shinyapps.io/Dev_data_products_final_project/)*

